---
title: "Tidy Tuesday 2019_04_16"
author: "Rui Guo"
date: "2019/4/29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load all data

```{r load all data}
library(tidyverse)
library(mapdata)
brexit <- read_csv("data/brexit.csv")
corbyn <- read_csv("data/corbyn.csv")
dogs <- read_csv("data/dogs.csv")
eubalance <- read_csv("data/eu_balance.csv")
pensions <- read_csv("data/pensions.csv")
trade <- read_csv("data/trade.csv")
women_research <- read_csv("data/women_research.csv")

```

# Question 1: In data brexit.csv, guess how britain think about exit EU?

```{r}

brexit_long <- gather(brexit, key = "br_choose",value = "percent", -date, factor_key = TRUE)

q1_plot_1 <- ggplot(brexit_long, aes(x= as.Date(date, "%d/%m/%y"),y = percent, color= br_choose))+
  geom_line()+
  labs(title = "Should Britain exit from EU?", x= "Date", y = "Percent", color = "Responding")+
  scale_color_manual(labels=c("Right","Wrong"), values = c("green", "red"))+
  geom_smooth(method = lm, se = F,size = 4)+
  theme_bw()

q1_plot_1

```

# Question 2: In data brexit.csv, devide time to 4 stage, what is the choose in last day of each stage.

```{r}

rows <- nrow(brexit)

brexit_stage <- brexit[c(1, rows%/%3, rows%/%3*2, rows), ]

brexit_stage <- brexit_stage %>% 
  mutate(other = 100-percent_responding_right-percent_responding_wrong,
         date = as.factor(date))

brexit_stage_long <-gather(brexit_stage, key="type", value = "percent", -date) 

q2_plot_1 <- ggplot(brexit_stage_long, aes(x= "content",y = percent, fill = type))+
  geom_bar(stat = "identity", position = "stack", width = 1)+
  facet_grid(~as.factor(as.Date(date, "%d/%m/%y")))+
  coord_polar(theta = "y")

q2_plot_1


```

#### To make it looks better....

```{r}

q2_plot_2 <- ggplot(brexit_stage_long, aes(x = type, y = percent, fill = type)) +
  geom_bar(stat = "identity", alpha= 0.7)+
  coord_polar()+
  facet_grid(~as.factor(as.Date(date, "%d/%m/%y")))+
  labs(x = "", y = "")+ 
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(),
        legend.position = "none")

q2_plot_2  


q2_plot_3 <- ggplot(brexit_stage_long, aes(x = type, y = percent, fill = type)) +
  geom_bar(stat = "identity", alpha= 0.7)+
  coord_polar(theta = "y")+
  facet_grid(~as.factor(as.Date(date, "%d/%m/%y")))+
  labs(x = "", y = "")+ 
  theme(axis.text = element_blank(), 
        axis.ticks = element_blank(),
        legend.position = "none")

q2_plot_3 

```

# Question 3: in data corbyn.csv, which political or group is the popular on Facebook?
  <font color = blue> Want to draw a average value as a refrence line</font> 

```{r}
q3_plot_1 <- ggplot(corbyn, aes(x=political_group, y = avg_facebook_likes, fill = political_group))+
  geom_bar(stat = "identity")+
  geom_hline(aes(yintercept = mean(avg_facebook_likes)))+
  theme(axis.text.x = element_text(angle = 90))

q3_plot_1
```


# Question 4: In Data dog.csv, does people like small dog more than big dog?


```{r}

q4_plot_1 <- ggplot(dogs, aes(x=year, y = avg_weight))+
  geom_path()

q4_plot_1

```
    


# Question 5: Which country balance become to better?
#### Draw a graph for only one country first.

```{r}
Spain <- subset(eubalance, country == "Spain")

Spain$pos <- Spain$value >= 0

q5_plot_1 <- ggplot(Spain, aes(x = year, y = value,fill = account_type, ))+
  geom_bar(stat = "identity", position = "dodge")+
  labs(title = "Spin balance", subtitle = "2009-2015", x="year", y="balance", fill = "type")
  
q5_plot_1

```

# Question 6: Which country support old people more than other country?

```{r}
```


```{r}
pensions$rate <- pensions$gov_spend_percent_gdp/pensions$pop_65_percent

q6_plot_1 <- ggplot(pensions, aes(x = round(pop_65_percent) , y =country ))+
  geom_tile(aes(fill=rate))
q6_plot_1

```

#### Work with map.

# Question 7: Which field is women work with?

```{r Question plot}

q7_1 <- ggplot(women_research, aes(x = field, y = percent_women))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90))
  
q7_1

```

#### To make it better...

```{r}
q7_2 <- ggplot(women_research, aes(x = field, y = percent_women, color = field))+
  geom_boxplot()+
  theme(axis.text.x = element_text(angle = 90))+
  scale_color_manual(values = c("black", "black", "red", "black","black"))  
    
q7_2
```

# Question 8: Which country is lost of women go to work?

#### In this case I learn how to mean by row in 

```{r}
women_research_wide <- spread(women_research, field, percent_women) 

women_research_wide$avg <- rowMeans(women_research_wide[, -1])

q7_3 <- ggplot(women_research_wide, aes(x = country, y = avg, size = avg, color = country))+
  geom_point()
q7_3
```


#### In this case learn how to draw data in real map.

```{r}
world <- map_data("world")

ww <- left_join(world, women_research_wide, by = c("region" = "country"))

q7_4 <- ggplot(ww, aes(x=long, y = lat, group = group))+
  geom_polygon(aes(fill = avg))+
  scale_fill_viridis_c()

q7_4
```


